Gravitational-wave sensitivity curves

### 2014-08-06 Detectors.tex
GEO related things

The most notable ground-based detectors are LIGO and Virgo, which work in collaboration, supported by GEO600. LIGO, Virgo and GEO600 have completed science runs as first-generation detectors \cplb{[citation needed]}. As LIGO and Virgo are currently being upgraded their initial configurations are now referred to as Initial LIGO (iLIGO) and Initial Virgo (iVirgo) respectively. The upgraded, second-generation versions are referred to as Advanced LIGO (aLIGO) and Advanced Virgo (AdV) respectively. LIGO has two observatories: one at Hanford, Washington, which has two detectors; and another at Livingston, Louisiana. There is an agreement to move one of the upgraded Hanford detector systems to a location in India \citep{LIGO-India,Unnikrishnan2013}. The GEO600 detector can also operate in a high frequency mode \citep[GEO-HF]{2006CQGra..23S.207W} \cplb{Add to table}. The advanced detectors should start operation in the next couple of years, with LIGO-India following further in the future.

>>>>

The most notable ground-based detectors are LIGO and Virgo, which work in collaboration, supported by GEO600. LIGO, Virgo and GEO600 have completed science runs as first-generation detectors \citep[e.g.,][]{Abadie2010}. As LIGO and Virgo are currently being upgraded their initial configurations are now referred to as Initial LIGO (iLIGO) and Initial Virgo (iVirgo) respectively. The upgraded, second-generation versions are referred to as Advanced LIGO (aLIGO) and Advanced Virgo (AdV) respectively. LIGO has two observatories: one at Hanford, Washington, which has two detectors; and another at Livingston, Louisiana. There is an agreement to move one of the upgraded Hanford detector systems to a location in India \citep{LIGO-India,Unnikrishnan2013}. The GEO600 detector is not subject to a major upgrade plan, but since summer 2009 it has enhanced by a series of smaller improvements, notably improving high-frequency sensitivity \citep[GEO-HF;][]{2006CQGra..23S.207W}. The advanced detectors should start operation in the next couple of years, with LIGO-India following further in the future.
